% Resume
\documentclass[11pt,a4paper]{article}

% ---------- Packages ----------
\usepackage[left=1in, right=0.5in, top=0.5in, bottom=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}
\usepackage{setspace}
\usepackage[none]{hyphenat}


% ---------- Formatting ----------
\setstretch{1.05}
\titleformat{\section}{\Large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0mm}{5mm}{3mm}
\titlespacing{\subsection}{0mm}{3mm}{1mm}

\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=10mm}

\hyphenpenalty=10000
\exhyphenpenalty=10000
\emergencystretch=3em
\tolerance=2000
\pretolerance=1000



\pagenumbering{gobble}

\begin{document}

\noindent
{\Large \bf Pushpkant Yadav}\\[1mm]
{\bf System Architect - Embedded Systems \& Digital Twin Platforms
}
\\[2mm]
\href{mailto:pushpkantyadav@gmail.com}{pushpkantyadav@gmail.com} $\;|\;$
+91-9950238365 $\;|\;$
\href{https://www.linkedin.com/in/pushpkant-yadav-11196960/}{LinkedIn} $\;|\;$
\href{https://github.com/Pushpkant}{GitHub}
\\[2mm]
{\bf
Architecting digital twins of complex avionics LRUs for early hardware–software co-design and system bring-up.
}

\section*{Professional Summary}
System Architect with 13+ years of experience designing and validating complex embedded systems, with a strong focus on digital twins and virtual platforms for avionics LRUs. Experienced in architecting QEMU-based MPSoC system models to support early software development, driver validation, and system bring-up ahead of hardware availability. Strong background in Embedded Linux, Zynq UltraScale+ MPSoC architecture, hardware–software co-design, and system-level debugging. Drives architectural proof-of-concepts, resolves high-impact technical risks, and mentors engineers across disciplines.


\section*{Core Skills}
\subsection*{System Architecture, Digital Twin \& Leadership}
Embedded systems architecture, digital twin \& virtual platforms, avionics LRU systems, hardware–software co-design, architectural definition \& design reviews, proof-of-concepts, technical risk assessment, cross-functional technical mentoring.

\subsection*{Simulation \& Modeling}
QEMU (board \& peripheral modeling), virtual prototyping, system-level modeling (UML), pre-silicon / pre-hardware validation, SystemC (TLM 2.0 – working knowledge), transaction-level modeling (conceptual).

\subsection*{Platforms, Processors \& Software}
Zynq UltraScale+ MPSoC (Cortex-A53 / R5 / PL), ARM Cortex-A/R/M, RISC-V (bare-metal \& RTOS), Embedded Linux, Yocto (PetaLinux, Processor SDK Linux), BSP \& boot flow bring-up, Linux device drivers, memory map, interrupts \& DMA, system debugging \& root-cause analysis.

\subsection*{FPGA, Interfaces \& Timing}
Vivado Design Suite, AXI bus architecture, custom PL IP integration, Verilog (design review \& debug level), SPI, I2C, UART, PCIe, USB, Ethernet, IEEE-1588 PTP, NTP, GPS.


\section*{Work Experience}

\subsection*{Honeywell Technology Solution}
System Architect - Embedded Systems \& Digital Twin Platforms\\
Sep 2024 - Present
\begin{itemize}
\item 
Architecting QEMU-based digital twins of aerospace avionics LRUs built on Zynq UltraScale+ MPSoC platforms to enable early hardware–software co-design and system-level validation.
\item 
Defined system architecture and abstraction strategies for modeling MPSoC processing systems, programmable logic interfaces, and multiple COTS peripherals within the virtual platform.
\item 
Enabled Embedded Linux boot, driver validation, and application bring-up on virtual platforms ahead of physical hardware availability, significantly reducing dependency on additional hardware for development and validation.
\item 
Led architectural proof-of-concepts and resolved complex system-level issues spanning simulation models, boot flows, and low-level software interactions.
\item 
Developed an architectural proof-of-concept simulating MPSoC RPU execution in QEMU with selected PL peripherals modeled in SystemC, including functional synchronization between QEMU and SystemC for system-level digital twin validation.
\item 
Architected a Linux-based, multi-tenant simulation platform enabling thousands of users to execute virtual system simulations remotely, providing a scalable alternative to physical hardware test benches.
\item 
Extended the simulation platform to support remote debugging workflows, enabling users to attach local debuggers to virtual targets and use the simulator as a functional replacement for physical test benches in VectorCast-driven execution environments.
\item 
Designed and validated scalable simulation capacity, supporting approximately 500–600 concurrent virtual instances for lightweight systems and 100–150 instances for hardware-intensive configurations per server.
\item 
Collaborated with and mentored FPGA, hardware, and software teams on MPSoC architecture, virtual platform workflows, and system-level debugging.
\end{itemize}

\subsection*{Logic Fruit Technologies}
Project Lead – Embedded Systems\\
Sep 2021 – Sep 2024

\begin{itemize}
\item Led system architecture and Embedded Linux platform development for complex telecom and defense-grade embedded systems.
\item Designed and integrated MPSoC- and FPGA-based platforms, including device drivers, BSP bring-up, and high-speed interface integration.
\item Architected and implemented IEEE 1588 Precision Time Protocol (PTP) solutions for timing-critical systems, including PHC clock integration and driver support.
\item Mentored engineers across software, FPGA, and hardware domains, driving architectural reviews and technical decision-making.
\end{itemize}

\subsection*{Noble Labs}
Embedded Systems Consultant / Projects Leader (Owned Firm)\\
Feb 2018 – Sep 2021

\begin{itemize}
\item Architected and delivered end-to-end embedded systems spanning hardware, firmware, and Embedded Linux platforms.
\item Led system bring-up, validation, and customer-facing technical engagements across multiple embedded product domains.
\end{itemize}

\subsection*{NeuroEquilibrium Diagnostic Systems Pvt. Ltd.}
R\&D Manager / Senior Embedded Engineer\\
Jun 2015 – Feb 2018

\begin{itemize}
\item Designed and validated real-time embedded systems for medical diagnostic devices, integrating sensors, control systems, and signal processing pipelines.
\item Led architecture definition and system-level debugging for safety- and reliability-critical embedded products.
\end{itemize}

\subsection*{CadBridge Semiconductor Pvt. Ltd.}
Junior Embedded Systems Engineer\\
Feb 2013 – May 2015

\begin{itemize}
\item Developed low-level firmware and hardware interface code for embedded platforms, building a strong foundation in system bring-up and debugging.
\end{itemize}

\section*{Education}

M.Tech – Embedded Systems, BITS Pilani (WILP), 2025\\
B.Tech – Electronics \& Communication Engineering, RTU, 2011


\end{document}